A Gambler's DAgger: Reducing Supervisor Burden in Online Learning From Demonstration Learning Through Hierarchical Supervisors

### 2016-02-22 paper.tex
stuff

\begin{abstract}
Online learning from demonstration algorithms such as
DAgger can learn policies for problems where the system dynamics and
the cost function are unknown. However they impose a
burden on supervisors to respond to queries each time the robot
encounters new states while executing its current best policy.  Traditionally there has only been one supervisor and it is deemed expert. However, an expert supervisor might not be needed for a large portion of the state space, which could be handled by less-skilled supervisors. We present the Gambler's DAgger, which instead of only using an expert supervisors presents a hierarchical supervisor model, which first leverages cheaper supervisors, such as analytical methods on approximate dynamics or crowdsourced Amazon Mechanical Turk workers to train the policy and then only consults an expert for harder to learn states. We demonstrate this approach in training a visuomotor deep network policy for 2D grasping in clutter on a 4-DOF Zymark Robot. We were able to reduce the number of queries to the final expert supervisor by $X$ and manage to collect $X$K examples by leveraging the hierarchical supervisor model. 
 \end{abstract}

@@

\section{Related Work}
Below we summarize related work in reducing the number of queries to an expert in the Online LfD setting.\mlnote{Still a work in progress}

@@

@@

\caption{\footnotesize  The interface AMT workers see for providing feedback to the robot for the grasping in clutter task. The pink overlay indicates the desire change in the robot position with respect to the current robot state. Then AMT workers can use their intuition for how objects respond to force to provide examples of how the robot should behave. Each window shows a correction in a degree of freedom a) is the rotation of the robots base b) is extending the robot's arm c) is closing the gripper and d) is rotating the turn table}
\vspace*{-20pt}
\label{fig:overlays}
\end{figure*}

@@

\subsection{Task}
We are interested in training a Zymark \mlnote{need make and model} to perform a grasping in clutter task on image data taken from a Logitech 2000 camera. Examples of images from the camera can be seen in Fig. \ref{fig:teaser}.

@@

\noindent \textbf{Expert Supervisor} Finally after training with the Analytical and Crowdsourced Supervisor we leverage the Expert supervisor, who is capable of achieving high cumulative reward but is a limited resource, to provide corrections for a problem that would be non-obvious for someone who doesn't understand the physical limiations of the problem. Examples of this could be joint limits of the robot or how some of the objects might respond in more advanced dynamics. \mlnote{After we run the AMT study it will become apparent where an expert is still needed}

It can still be hard for an expert to provide the correct feedback without knowing the magnitude of the controls suggested, so they use the same interface as the CrowdSource Supervisor.

@@

\section{Experiments}

\mlnote{We need to nail down exactly what experiments are important. I suggest 1) main one is to show expert time withouth bootstrapping vs. with 2) can be different forms of how to handle the dataset aggregation (i.e. full retrain or batch update etc.) 3) analysis of the crowd source system and how effective that was (this would be a secondary follow up experiment though, 4) Can be also comparison with a previous way to reduce supervisor burden in high dimensional states (i.e. SHIV). }

>>>>

\begin{abstract}
Online learning from demonstration algorithms such as
DAgger can learn policies for problems where the system dynamics and
the cost function are unknown. However they impose a
burden on supervisors to respond to queries each time the robot
encounters new states while executing its current best policy.  Traditionally there has only been one supervisor and it is deemed expert. However, an expert supervisor might not be needed for a large portion of the state space, which could be handled by less-skilled supervisors. We present the Gambler's DAgger, which instead of only using an expert supervisors presents a hierarchical supervisor model, that first leverages cheaper supervisors, such as analytical methods on approximate dynamics or crowdsourced Amazon Mechanical Turk workers to train the policy. Then only consults an expert supervisor for harder to learn states. We demonstrate this approach in training a visuomotor deep network policy for 2D grasping in clutter on a 4-DOF Zymark Robot. We were able to reduce the number of queries to the final expert supervisor by $X$ and manage to collect $X$K examples by leveraging the hierarchical supervisor model. 
 \end{abstract}

@@

\section{Related Work}
Below we summarize related work in reducing the number of queries to an expert in the Online LfD setting.\mlnote{Still adding to this}

@@

\mlnote{we can formally prove the following statements or point to the web similar to SHIV... it will be more trivial to write these out though if we have space}
With respect to the theoretical analysis of DAgger's convergence rate, one can see that in our algorithm you are solving $M$ individual DAgger's ~\cite{ross2010reduction}. Thus, in the worst case you will converge to the supervisor at the top of the hierarchy $\tilde{\pi}_M$ in $\tilde{O}(M*T)$ iterations instead of DAgger's original $\tilde{O}(T)$.

It should be noted though that as you iterate through the hierarchy of supervisors, each iteration starts out with an error bounded by $\int_{\mathcal{X}_{m,m+1}} ||\pi_{\theta_{0,m+1}}(\mathbf{x}) - \tilde{\pi}_{m+1}(\mathbf{x})||^2_2 p(\mathbf{x}|\theta_{0,m+1}) d\mathbf{x} + \epsilon$. Thus, if the supervisors are able to agree on a large part of the state space, there should be less iterations with the expert supervisor than $\tilde{O}(T)$, which we experimentally show in our grasping in clutter task.

@@

\caption{\footnotesize  The interface AMT workers see for providing feedback to the robot for the grasping in clutter task. The pink overlay indicates the desire change in the robot position with respect to the current robot state. Then AMT workers can use their intuition for how objects respond to force to provide examples of how the robot should behave. Each window shows a correction in a degree of freedom a) is the rotation of the robots base b) is extending the robot's arm c) is closing the gripper and d) is rotating the turn table (WILL UPDATE THIS FIGURE)}
\vspace*{-20pt}
\label{fig:overlays}
\end{figure*}

@@

\subsection{Task}
We are interested in training a Zymark robot to perform a grasping in clutter task on image data taken from a Logitech 2000 camera. Examples of images from the camera can be seen in Fig. \ref{fig:teaser}.

@@

\noindent \textbf{Expert Supervisor} Finally after training with the Analytical and Crowdsourced Supervisor we leverage the Expert supervisor, who is capable of achieving high cumulative reward but is a limited resource, to provide corrections for states that would be non-obvious for someone who doesn't understand the physical limitations of the task. Examples of this could be joint limits of the robot or how some of the objects might respond in more advanced dynamics. \mlnote{After we run the AMT study it will become apparent where an expert is still needed}

It can still be hard for an expert to provide the correct feedback without knowing the magnitude of the controls suggested, so they use the same interface as the CrowdSourced Supervisor.

@@

\section{Planned Experiments}
All these experiments will be in the grasping clutter domain described above. This section is divided into experiments on reducing supervisor burden via hierarchical supervisor's and testing components on our large scale learning system.

\subsection{A Gambler's DAgger}

\noindent \textbf{Reducing Supervisor Burden}
In this experiment, we will assign some cost to each supervisor Analytical could be 0.5, Crowdsource 2, and Expert 10 for example. Then compute how many times the expert had to of been queried by using the bootstraped method. We will then do a full DAgger with our experts for comparison to when you don't bootstrap.

\noindent \textbf{When this Won't Work}
In this experiment, we will look at using two analytical supervisors to try and teach the robot, however they will violate the definition of and not have an overlapping policy (need to think about this a bit). We should see that the supervisor deemed higher in the heirachy has to do roughly if not more queries than without bootstrapping.

\subsection{System Experiments}

\noindent \textbf{Finding a Neural Network Architecture for Policy Learning}
I want to determine if we can use our analtyical method to find the right architecture by iterating through a dataset. The hypothesis is that you do not need to do roll-outs if you change architecture slightly for better performance (i.e. can I collect a data from rolling out when network and then iterate on that dataset to find the best architecture)

We will see how close a different architectures who received lower training loss on the dataset are to the original trained network in terms of euclidean distance.

\noindent \textbf{Reliability of Crowdsourced Supervisors}
This experiment is more of a study looking for a few factors, how much data can we get, what is the price point and how lower quality is it to the expert.

Anca and I discussed an experiment to measure performance against expert. We can then just report our observations in terms of data gathered, time it took and price paid.
